Check Coverage

### 2019-07-02 analysis/coverage_check.Rmd
Check coverage for mammals and get id counts for all species (not just birds and mammals).

check if all bird & mammal biotime data w/id's has an elton match. There are 81 species without a match (67 are birds).
```{r}
no_trait <- biotime_data %>%
  #filter(taxa == "Birds") %>%
  select(id, taxa) %>%
  drop_na(id) %>%
  distinct() %>%
  filter(!id %in% elton_bird$id, !id %in% elton_mamm$id)

@@

and 552 species without an ID, some of which are species codes
```{r}
biotime_data %>%
  #filter(taxa == "Birds") %>%
  select(id, matchingName, taxa) %>%
  distinct() %>%
  filter(is.na(id)) %>%
  dim()
```

@@

coverage <- bird_data %>%
  group_by(study_id) %>%
  summarise(perc = sum(!is.na(specid))/n()) %>%
  arrange(desc(perc))

head(coverage)
```

>>>>

check if all bird & mammal biotime data w/id's has an elton match. There are 63 species without a match (54 are birds).
```{r}
no_trait <- biotime_data %>%
  filter(taxa %in% c("Birds", "Mammals")) %>%
  select(id, matchingName, taxa) %>%
  drop_na(id) %>%
  distinct() %>%
  filter(!id %in% elton_bird$id, !id %in% elton_mamm$id)

@@

and 20384 species without an ID, some of which are species codes
```{r}
biotime_data %>%
  #filter(taxa == "Birds") %>%
  select(id, matchingName, taxa) %>%
  filter(is.na(id)) %>%
  distinct() %>%
  dim()
```

@@

mamm_data <- biotime_data %>%
  filter(taxa == "Mammals") %>%
  left_join(elton_mamm, by = "id",
            na_matches = "never")

bird_coverage <- bird_data %>%
  group_by(study_id) %>%
  summarise(perc = sum(!is.na(specid))/n()) %>%
  arrange(desc(perc))

mamm_coverage <- mamm_data %>%
  group_by(study_id) %>%
  summarise(perc = sum(!is.na(msw3_id))/n()) %>%
  arrange(desc(perc))

head(bird_coverage)
head(mamm_coverage)
```
